Program Optimisations via Hylomorphisms for Extraction of Executable Code

### 2025-07-07 paper/paper.tex
minor

%Editor-only macros:: begin (do not touch as author)%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\EventEditors{}
\EventNoEds{2}
\EventLongTitle{ITP 2025)}
\EventShortTitle{ITP 2025}
\EventAcronym{ITP}
\EventYear{2025}
\EventDate{December 24--27, 2016}
\EventLocation{Little Whinging, United Kingdom}
\EventLogo{}
\SeriesVolume{42}
\ArticleNo{23}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

For example, the category of sets, denoted by $\Set$, is the category where
objects are sets and arrows are functions between sets. The initial object $0$
in $\Set$ is the empty set $\emptyset$ and the terminal object $1$ is any
singleton set. The reader who is not accustomed with category theory can assume
types are sets, giving the intuition that the category $\Set$ can also be viewed
as the category of (simple) types and programs between them.

>>>>

%Editor-only macros:: begin (do not touch as author)%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\EventEditors{Yannick Forster and Chantal Keller}
\EventNoEds{2}
\EventLongTitle{16th International Conference on Interactive Theorem Proving (ITP 2025)}
\EventShortTitle{ITP 2025}
\EventAcronym{ITP}
\EventYear{2025}
\EventDate{September 29--October 2, 2025}
\EventLocation{Reykjavik, Iceland}
\EventLogo{}
\SeriesVolume{352}
\ArticleNo{32}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

For example, the category of sets, denoted by $\Set$, is the category where
objects are sets and arrows are functions between sets. The initial object $0$
in $\Set$ is the empty set $\emptyset$ and the terminal object $1$ is any
singleton set. The reader who is not accustomed with category theory can assume
types are sets and programs are functions, giving the intuition that the category $\Set$ can also be viewed as the category of (simple) types and programs between them.
